A graph-based data model for interactive evolutionary computation

### 2017-01-20 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Basic description of case study
Gammification Techniques explained, to do: Set-up and Results.

\section{IEC Graph Conceptual Model}

@@

\item Users. This nodes represent the human users of the system and have 
the attributes: {\tt id} a unique identifier, {\tt name}  and {\tt created}
specifing the  creation date (time stamp) of the node.

\item Individual. This type of node has the following attributes: 
{\tt id}, {\tt chromosome}  and {\tt views} this is 
the amount that users have seen or interacted with this individual and
 {\tt created}.
\item Collection. This type of nodes represent the collections belonging
to users, their attributes are {\tt id}, 
{\tt name}, {\tt created} and {\tt is_private} indicating if this collection
contents are shared with others. 
\end{itemize}

\subsection{Relationship Types}
%%
%% Explain relations

The {\tt likes} relation describes the interaction between a User and
an Individual in which a rating value is assigned. In the current application
a user is allowed to rate an Individual multiple times, so the date of the 
interactions is also of interest.

\begin{itemize} 
\item id. 
\item created. 
\item rate.
\end{itemize}

The relation {\tt knows} connects two users that know each other. This relation
is "unique" meaning that it can not be repeted between a pair of nodes.  
The relation {\tt parent} describes what Individual is the parent of a new
Individual and is also unique.  
The relation {\tt has} describes an ownership relation between users and
those collections they own. Also a collection {\tt has}  individuals stored
in them.

In figure \ref{fig:Has_edge} the {\tt has} relationship 
between certain nodes $user$, $individual$ and $collection$ is shown.

\begin{figure}[!t]
    \centering
        \includegraphics[width=2.5in]{img/edge_properties_has.png}
    \caption{ The {\tt has} relationship type example and attributes.}
    \label{fig:evo}
\end{figure}

@@

>>>>

\section{IEC Graph Data Model}

@@

\item {\bf Users} This nodes represent the human users of the system and have 
the attributes: {\tt id} a unique identifier, {\tt name}  and {\tt created}
specifing the  creation date (time stamp) of the node.

\item {\bf Individual} This type of node has the following attributes: 
{\tt id}, {\tt chromosome}  and {\tt views} this is 
the amount that users have seen or interacted with this individual and
 {\tt created}.

\item {\bf Collection} This type of nodes represent the collections belonging
to users, their attributes are {\tt id}, 
{\tt name}, {\tt created} and {\tt is\_private} indicating if this collection
contents can be are shared with others. 
\end{itemize}

\subsection{Relationship Types}
%%
%% Explain relations
\begin{itemize}
\item {\bf Likes} This relation describes the interaction between a user and
an individual in which a rating value is assigned this is represented by 
the {\tt rate} attribute. In the current application a user is allowed to rate
an individual multiple times, so the date of the interactions is also of
interest.

\item {\bf Knows} The relation connects two users that know each
other. This relation is "unique" meaning that it can not be repeted between a pair of nodes.

\item {\bf Parent} Describes what individual is the parent of a new individual and is also unique.

\item {\bf Has} The relation describes an ownership relation between users and
those collections they own. Also a collection {\tt has}  individuals stored
in them.  In figure \ref{fig:has} the {\tt has} relationship 
between certain nodes $user$, $individual$ and $collection$ is shown.

\item {\bf Shared} When a user takes an individual from a friends collection, this interactions is described by a {\tt share} relationship, between the user and the individual.

\item {\bf Saved} When a user takes an individual from the wall interface, this 
interactions is described by a {\tt save} relationship. 
\end{itemize}

\begin{figure}[!t]
    \centering
        \includegraphics[width=2.5in]{img/edge_properties_has.png}
    \caption{ The {\tt has} relationship type example and attributes.}
    \label{fig:has}
\end{figure}

Is important to notice that this model is still partial view of the IEC system,
and other models can could be used in practice when implementing the system. 
For instance a relational database can be used for the implementation of a
user profile and authentication module. Also a copy or cache of the population 
could be kept in a key-value store in memmory for performance reasons. 
Nevertheless, the model can give important insights of the behaviour of the 
system.

@@

We present in this section the results of a comparassion between two versions
of the same IEC application. The goal of the experiment is to compare two 
gamification techiniques to increase volunteer participation. 
The main difference between both versions is how the fitness of individuals
is calculated and the information presented to users. 
\subsection{Gamification technique}
\label{sec:gamification}
The gammification technique
consists in giving more importance to the preference of users with more
participations. A feature found in video games is the concept of a 
score and experience levels. Levels depend on the score and certain features
of the game are only available to gamers when they reach a giving level.

The score achieved by users depends on the actions he does in the system as
each time a user does one of these actions their score is incremented by one.
The actions considered in this application are: 
\begin{itemize}
\item Start a session.
\item Rate an individual.
\item Create a collection.
\item Save an individual of the wall to a collection.
\item Save an individual from a friend's collection.
\item Explore collections of other friends.
\end{itemize}
Only the "Start a session" and "Explore collections of other friends". 
Are not found in the graph model, 
%% Note: I must ask Christian where they are stored 
%%

The weight of the preference of a users can depend on two scores:
\begin{itemize}
\item Experience. This value depends on the score and is a value 
between 0 and 100.

\item Participation. This value is simply the degree of the user node 
in the graph. This measure also considers the number of users he knows,
perhaps some of the users where invited to the system by him.   
\end{itemize}

The comparation consisted on three versions:
\begin{itemize}
\item Non Gammification. All users have the same weight.
\item Non Graph Gammification. Only experience is considered
\item Graph Gammification. Both experience and participation where considered.
\end{itemize}
When gammification was employed, all score values known where presented to users
and a ranking of users by weight was shown in a window, a screen capture of
this interface is shown in figure \ref{fig:top-users}.

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{Sample of users, showing the {\tt knows} relationship.}
    \label{fig:top-users}
\end{figure}

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/leaderBoard.png}
    \caption{User interface showing top users.}
    \label{fig:top-users}
\end{figure}

\subsection{Set-up}
\label{sec:setup}

\subsection{Results}
\label{sec:results}

\begin{figure*}[!t]
    \centering
        \includegraphics[width=3.5in]{img/comparison.png}
    \caption{Top ranked number individuals rated by user using a
     logarithmic scale.}
    \label{fig:top-ranked-participation}
\end{figure*}
